A Fully Decentralized Infrastructure for Subscription-based IoT Data Trading

### 2020-08-14 ASRLab_Thesis_Template/thesis/thesis.tex
Add DOI
Chinese comma tweak
Minor fixes

% ------------------------------------------------
%                   DOI Watermark
% ------------------------------------------------
%\usepackage{draftwatermark}  % For DOI watermark
\usepackage{listings, makecell, multirow, hhline}
\usepackage{amsmath}
\usepackage[customcolors]{hf-tikz}

@@

\begin{document}
%\ShowDOI{doi:XXXX/NCKU2019XXXXX}

@@

在物聯網場景中，machine-to-machine（M2M）的發展勢不可擋，它允許機器擁有自己的數位資產並開始參與經濟活動，讓裝置間可以共享和交易其資源。在發布/訂閱（publish/subscribe）通訊模型上將及時資料貨幣化，就可以依據資料使用量來計費，這類似於軟體即服務 (Software-as-a-Service)，一種基於訂閱的定價模型。這種定價模型讓資料提供者可以更好地管理預算，且資料消費者可以隨興的訂閱和退訂。然而，動態的資料流提升了資料所有權和身份驗證的重要性和難度。因此，一個不需信任單一機構的資料交易基礎建設是必需的，除了能允許參與者進行交易，還能驗證資料所有權和完整性。此外，訂閱流程的自動化亦是資料貨幣化中至關重要的。在本文中，我們利用分散式帳本技術 (Distributed Ledger Techonology)，在 IoT 中介基礎架構之上構建去中心化資料交易平台。這種方法可以有效地提高運作透明度和系統可擴展性，建立在加密訊息協議之上的存儲允許在沒有權限的情況下通過分散式帳本儲存、傳輸、存取和驗證資料流，在我們的設計中也讓交易參與者的數位權益得到保證。

@@

\par{\noindent \bf 關鍵字:}{發布/訂閱, 資料交易, 去中心化, 分散式帳本技術}
\clearpage
\setstretch{1.2}

@@

%trustless & automated
%trust: 對系統、對身份、對資料
In data trading platforms, there are three major aspects that need trust: identity, data ownership, and trading. Proving the identity as well as the ownership of data is a challenging issue among various roles in a large scale platform. In current systems, a trusted third-party authority like certificate authority (CA) is widely adopted to certify each member. However, building trust upon CA is dangerous and fragile. The compromise of routers or CA can break the trust of the entire system, and the data portability of using third-party services is still under suspicion. Meanwhile, these concerns are taking into data storage as well, keeping data assets in a centralized data storage or a cloud service meet the constraints of data portability, which may violate the General Data Protection Regulation (GDPR)\cite{GDPR}. Besides CA and storage, the subscription history of data consumers may reveal his/her interests and the exposure of personal information during trading process against GDPR as well. The final trust is trading procedures, apart from setting up the agreement between providers and consumers, both of them need to confirm that the agreement will be executed even if one party fails to comply.

@@

Taking all the requirements and the features of streaming data into consideration, the data trading platform for IoT towards a decentralized and trustless design. In this paper, we investigate the use of a decentralized publish/subscribe (pub/sub) model and DLTs to construct the authority-less and trusted infrastructure. See Fig.~\ref{fig:system_design}. The pub/sub model features the scalability and resource-efficiency, and DLTs resolve the trust of the service, since data and contracts (i.e., smart contracts) written on DLTs are transparent, immutable, and enforced automatically, the digital rights of participants are protected. Lastly, an end-to-end encrypted transmission protocol built on top of DLT is used as data storage, which not only ensures the data integrity but also enables access control and provides a scalable key and data management.

\subsection{Contributions}
The contributions in the thesis are summarized as follow:
\begin{itemize}
    \item We investigate the usage of DLTs and distributed data storages in order to propose a decentralized architecture for IoT trading and to enable participants to automate the trading procedures and secure digital assets exchange across different organizations.
    \item We apply the subscription-based services economic model to adapt the features of IoT streaming data and clarify the importance of using a decentralized identity system for trading.
    \item We evaluate the performance and concerns of adopting an end-to-end encrypted transmission protocol, and propose an alternative approach for low-level devices to adopt this protocol while ensuring the privacy.
    \item We analyze the cost of the designed smart contract to estimate the minimum data product price for data providers to sustain a product and the minimum cost for data consumers to interact with data products.
\end{itemize}
\clearpage

\subsection{Thesis Organization}
The rest of this thesis is organized as follows. In Section~\ref{section:relatedWork}, some related work of pub/sub over blockchain, decentralized data trading infrastructures, and distributed data storage are analyzed. In Section~\ref{section:design_thinking}, the components of proposed subscription-based data trading architecture is illustrated. In Section~\ref{section:MAM}, the end-to-end encrypted transmission protocol is introduced along with the protocol delegation solution for low-level devices. In Section~\ref{section:trading_model}, the trading models of proposed architecture are well explained. The analysis results are given in Section~\ref{section:evaluation}. Finally, we conclude the thesis in Section~\ref{section:conclusion} and the future work in Section~\ref{section:future_work}.

@@

\subsection{The Publish/subscribe Communication Models Over Blockchain}
The pub/sub service model consists of publishers, subscribers, and brokers, which has been proven\cite{pubSubAnalysis, pubSubAnalysis2} to be an efficient and flexible solution for a large number of diverse entities like IoT applications. A lot of work in the pub/sub system built on top of blockchain focused on the reliability, scalability, and the different security issues such as, encrypted data communication, privacy-preserving data subscription, and access control of the digital asset.

@@

In \cite{userCentricData}, the publisher runs a node in blockchain that preserves all the history data of the ledger, therefore, they can publish and manage data without any third-parties. The subscribers request publisher directly and ask them to save a cache space for interesting data. The main contribution of the system is to ensure data owners have full controls of produced data, but the data owners need to have well devices and environments to perform such functionalities and preserve data. Also, the rights for accessing digital assets are more compatible in the IoT scenarios instead of copying raw data. Secure Pub-Sub model\cite{SPS}, a brokerless of pub/sub model, is proposed to eliminate the security risk of middleware in the model and to provide a reputation-based fairness payment strategy on blockchain. The privacy and data security are considered thoroughly with the encryption scheme, while the reputation of publishers, payment, and data sharing are deployed on smart contracts that allow all operations are transparent. The reputation system and the punishment rules against malicious acts of subscribers and publishers. Yet, without brokers, providers and subscribers may need to reveal more sensitive information like IP address in order to match both sides. Another broker-less model in \cite{PrivacyPreservPubSub} protects the subscribers' privacy by encrypting users' interests with the light-weight PKEwET\cite{PKEwET}, which allows publishers to match the subscribers' interests in the ciphertext.

@@

\subsection{Trusted IoT Trading Infrastructure}
Multiple infrastructures for trusted IoT data trading have been proposed by Paolo Missier et. al\cite{MindMyValue} presenting an IoT brokered infrastructure based marketplace that enables trading with Ethereum smart contracts. The brokers are only responsible for data transmission in order to adapt flexible agreement between participants. Unlike the standard pub/sub model that matches publishers and subscribers that participants are unaware of each other. However, the data cubes (i.e., a tuple of information, such as provider, subscriber, and time period) are stored in a centralized Cassandra NoSQL database, which is guaranteed to be tamper-proof but the risk of single-point failure still exists.

@@

\subsection{Distributed Storage System}
\label{section:distributed_storage}
Decentralized storage systems allow users to store files in a distributed network that is maintained by individual nodes around the world instead of a central service provider. Nevertheless, DLTs are often used as the backbone of these systems like data storage and also an incentive layer to encourage people to get involved in the network.

@@

\begin{spacing}{2.0}
\label{section:design_thinking}
\subsection{Data Subscription-based Trading Platform Players}
There are three major roles, data providers, data consumers, and brokers which are similar to the pub/sub messaging model. But unlike the standard pub/sub model where brokers link the publishers and subscribers who are not aware of each other, in our proposed architecture, the brokers are only responsible for message delivery and essential verification processes. As shown in Fig.~\ref{fig:pub_sub_model}.

@@

We adopt the brokered infrastructure for three reasons. Firstly, it inherits the benefits from the standard pub/sub model which is more efficient than the request/response model specifically in a large scale system. Furthermore, if either side is offline, the proceeding tasks have to stop and start over. With brokers, the unfinished work can be cached or accomplished. Second, a fully decentralized architecture has difficulties to brings data providers and consumers together, both of them need to reveal more sensitive information, such as IP address, in order to build the communication tunnel. The existence of brokers resolved the privacy issue, as brokers are the bridges that link data providers and consumers, participants can trade with minimum information like its identifier and public key. Third, a refund process needs brokers to host and supervise the procedures in order to protect the rights of participants, which will be further discussed in Section.~\ref{section:refund}.

\subsection{Choice of Data Storage}
Data storage is the trust basis of data trading platforms where the data assets are reserved. Streaming data unlike a fixed set of data that can be verified by the hash of the whole pack of data, it consists of continually granular records of each time slot. Therefore, the verification such as, data integrity and source identity is narrow down to a data point as well. In our proposed architecture, we adopt MAM as data storage to resolve the challenges of managing and verifying data streams. MAM is the second layer data communication protocol built on top of IOTA\cite{IOTAwhitepaper} network, the Tangle, a feeless cryptocurrency designed for IoT, which introduces properties like publishing, classifying and tracking authenticated message streams. Carrying these properties, MAM is also appropriate for building a self-sovereign identity system where the identity information such as public key, unique identifiers of services and metadata are stored. One can easily prove himself by sharing the identifier on MAM without any authority.

Currently, considering the efficiency of uploading large files, IPFS performs better than MAM (i.e., writing contents to IOTA network). However, IOTA network scales when more users and transactions join, and the MAM operations can be delegated to powerful proxy servers which is illustrated in Section.~\ref{section:ta_endpoint}. Furthermore, adopting IPFS in IoT scenarios may meet the challenges of data loss and data retrieving efficiency.

@@

\begin{itemize}
    \item \textbf{Scalability}:
    \begin{itemize}
        \item Benefits from the underlying Tangle network, the system scales when more participants and more transactions join the network.
        \item For both data providers and consumers, MAM keeps the number of managed keys and data entry points as small as possible
    \end{itemize}    
    \item \textbf{Integrity}:
    \begin{itemize}
        \item Messages published to the Tangle are tamper-proof against malicious modification.
        \item Messages are signed with the keys pre-generated under Merkle signature scheme\cite{MSS} (MSS) that both keys and messages can be verified by participants.
    \end{itemize}
    \item \textbf{Confidentiality}:
    \begin{itemize}
        \item The encrypted data are uploaded that only participants that have keys can decrypt.
        \item The authorized users can retrieve data streams since data is written on the Tangle which can be queried as long as the IOTA network is alive.
        \item MAM provides forward-secrecy. The entry points of future data can be derived, but it's impossible to trace back those in the past. This feature prevents adversaries from retrieving published history even if the key is revealed.
    \end{itemize}
\end{itemize}

@@

\begin{figure}
    \centering
    \includegraphics[width=6.5in]{img/channel_and_key}
    \caption{Within MAM channel, the message publisher has 2 types of key, an encryption key for encrypting contents and a signature key per message for digital signatures. Subscribers can validate the message with signature keys and decrypt messages with encryption keys.}
    \label{fig:channel_and_key}
\end{figure}
\clearpage

\subsection{Digital Identity}
The digital identity represents entities and holds the digital assets within the digital world, it is important to prove and show the identity to others during interactions. We select the decentralized identity model rather than a centralized one for the concerns in Table.\ref{tab:did}.

@@

\subsection{Enable Automated Trading Process}
Ethereum is a cryptocurrency building on top of a public blockchain-based distributed ledger. It provides the smart contract, which is a protocol for formulating agreement on a blockchain that running on decentralized virtual machines. A smart contract can interact with other contracts, make decisions, store data, and transfer cryptocurrency. All the participants in Ethereum can verify and execute the contracts, and once the contract is triggered, it is uninterruptible and will be executed automatically without any third-parties.

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=5.5in]{img/smart_contract_mam}
    \caption{The information of identity and data streams are stored on the Tangle with MAM which is all recorded on Product Contracts. Participants can easily retrieve information via the Product Contract and proceed to trade. For signature validation check and further exchange encryption keys, the MAM channel ID of participants' DID document are written down, presented in blue color. The orange color stands for the information of data products, which includes the data stream channel/endpoint ID.}
    \label{fig:smart_contract_mam}
\end{figure}
\clearpage

@@

\subsection{Enable Computation Tasks Delegation to Broker with Privacy}
To manage data products and to benefit from trading, data providers have to interact with MAM and Ethereum smart contract while doing its original tasks. However, the limited resources of low-level devices should be used in their jobs instead of handling all trading processes. Therefore, the operations of MAM and smart contracts are better to be delegated to brokers. The delegation should ensure the privacy of data providers, for instance, brokers are asked to attach messages to MAM and record encryption keys to smart contracts without knowing the contents. The encryption key upload procedure is illustrated in Section.~\ref{section:launch_data_product}.

@@

\subsection{The Message Streams}
\label{section:mam_streams}
A channel/endpoint is a stream of MAM transaction bundles, which consist of signature and the masked message payload. To publish a MAM message to a channel, MAM deploys MSS to sign the message payload to the channel, where $channel\ ID = root$ i.e., the MSS Merkle root. The Merkle tree is generated with \textbf{seed}, an identifier of its owner in the IOTA protocol, represents the ownership of all things associated with the user in the IOTA ecosystem. Furthermore, the structure of channel/endpoint implements forward linking, each address of a message can be derived from the previous one that other entities can fetch the next payload. This design also brings the advantage of forward secrecy, where no one has access to the data back from his/her entry point. Figure.~\ref{fig:mam_structure} shows the structure of the MAM channel/endpoint.

@@

\subsection{Enable Access Control and Authentication}
\label{section:mam_functions}
The access control can be enabled via encryption with NTRU\cite{NTRU}, a quantum secure cryptosystem, or Pre-shared key (PSK), to prevent random users retrieving the data from channels. If the message payload is encrypted, subscribers are required for encryption keys to decode messages. The authentication in MAM includes two aspects: source and data. Source authentication ensures the message that originates from the claimed owner, and data authentication ensures the integrity of the data from the sender. These are achieved through the MSS and One-way hash functions by validating the signature added in the signature section of the MAM bundle. However, the size of Merkle Hash Trees, that is, the size of a channel/endpoint should be determined at the start. Thus, data providers need to first decide how to distribute data products into MAM channels/endpoints before uploading data.

\subsection{The Advantages of Adopting MAM in Subscription-based Data Trading Infrastructure}
\label{section:mam_features}
%scalability
\subsubsection{A Scalable Keys and Data Entry Points Management}
The importance of scalable key and data entry points management increases over time. In MAM, with an entry point (i.e., the address of transaction) and the encryption key, one can derive the following addresses of the transaction and retrieve data. To manage a data stream, the owner only needs to preserve 1 entry point and 1 encryption key in MAM, but $N$ entry points and 1 encryption key in other distributed storage.
\clearpage

%classify
\subsubsection{Data Streams Classification and Traceability}
The channel and endpoint structures enable users to be able to easily categorized data streams with respect to different types and usages. For instance, sensor devices like AirBox\cite{LASS}, collect environmental data, can split the statistics like PM 2.5 and humidity by time period into separate channels, which is useful for data providers to organize records and to pack into different data products. As for data traceability, users can easily track the footprints of data change logs as well as checking the validity of modifications with the signature.

\subsection{Delegate MAM operations to Tangle-accelerator}
\label{section:ta_endpoint}
MAM builds a secure and authenticated communication protocol on top of multiple cryptosystems, which low-level devices need to spend a lot of resources to apply it, and they may not even support built-in libraries in the regular operating systems. To overcome these concerns, we propose another approach that allows data providers to delegate the MAM operations to Tangle-accelerators, proxy servers with high computation power, which can accelerate the interactions with Tangle while ensuring the privacy of data providers. Fig.~ \ref{fig:ta_struct} shows the structure of Tangle-accelerator, and Fig.~\ref{fig:delegation} shows how data providers can adopt MAM.
\clearpage

@@

\subsubsection{Communication Protocol}
In the following sections, we refer to the low-level devices as \textbf{endpoint}s. MQTT\cite{MQTT} is chosen as the communication protocol, which requires fewer TCP packets and less traffic. The topic-based pub/sub pattern and lightweight packet that MQTT adopts would undoubtedly play an important role in endpoints with limited bandwidth. The pub/sub model decouples publishers and subscribers in many ways:

@@

\subsubsection{End-to-End-Encryption}
Introducing a proxy server to process all the cryptographic operations causes the proxy server or the middle man can easily tamper the message. To avoid such malicious operations during transmission, we introduce another lightweight end-to-end-encryption (E2EE) upon MAM protocol. The plaintext will be encrypted with this lightweight end-to-end-encryption. The E2EE process ensures only authorized subscribers can read the messages published on MAM.

%pic
\begin{figure}[h]
    \centering
    \includegraphics[width=\linewidth]{img/MAM_E2EE}
    \caption{The process of E2EE.}
    \label{fig:MAM_E2EE}
\end{figure}

In the Fig.~\ref{fig:MAM_E2EE}, we illustrate each step in the presented E2EE process. The details of steps are addressed below:

\begin{enumerate}
    \item Generate symmetric keys with the unique device identifier and Message Authentication Code (MAC) of the previous message. If the message is the genesis message, then sharing secret initialization information would serve as the MAC of the previous message. Key Derivation Function (KDF) is used to generate the symmetric keys.
    \item Compute the Message Authentication Code (MAC) of current message with the Hash-based Message Authentication Code(HMAC). Both plaintext and symmetric key would be given as parameters in HMAC.
    \item Apply the generated symmetric key to encrypt the plaintext.
    \item Concatenate the MAC of the current message would and the MAC of the previous message, and then the result will be signed with a digital signature algorithm.
    \item Send the ciphertext along with signed MAC.
\end{enumerate}

@@

The E2EE protocol presented in this paper combines a series of different cryptographic procedures. Each of them can be chosen on the basis of the working hardware and scenario by developers. On certain devices, hardware acceleration would be supported. With hardware-acceleration, the elapsed time could be dropped a step more. For example, applying AES-NI can accelerate AES operations around 40\% on Intel devices.\cite{AES-NI-Acceleration} According to Intel, Table~\ref{tab:AES_NI} shows the performance of Encryption of AES256 with and without hardware acceleration.

>>>>

% ------------------------------------------------
%                   DOI Watermark
% ------------------------------------------------
\usepackage{draftwatermark}  % For DOI watermark
\usepackage{listings, makecell, multirow, hhline}
\usepackage{amsmath}
\usepackage[customcolors]{hf-tikz}

@@

\begin{document}
\ShowDOI{doi:10.6844/NCKU202001948}

@@

在物聯網場景中，machine-to-machine（M2M）的發展勢不可擋，它允許機器擁有自己的數位資產並開始參與經濟活動，讓裝置間可以共享和交易其資源。在發布/訂閱（publish/subscribe）通訊模型上將及時資料貨幣化，就可以依據資料使用量計費，這是一種基於訂閱的定價模型，類似於軟體即服務 (Software-as-a-Service)。這種定價模型讓資料提供者可以更好地管理預算，且資料消費者可以隨興的訂閱和退訂。然而，動態的資料流提升了資料所有權和身份驗證的重要性和難度。因此，一個不需信任單一機構的資料交易基礎建設是必需的，除了能允許參與者進行交易，還能驗證資料來源和完整性。此外，訂閱流程的自動化亦是資料貨幣化中至關重要的。在本文中，我們利用分散式帳本技術 (Distributed Ledger Techonology)，在 IoT 中介基礎架構之上構建去中心化資料交易平台。這種方法可以有效地提高運作透明度和系統可擴展性，建立在加密訊息協議之上的存儲允許在沒有權限的情況下通過分散式帳本儲存、傳輸、存取和驗證資料流，在我們的設計中也讓交易參與者的數位權益得到保證。

@@

\par{\noindent \bf 關鍵字:}{發布/訂閱，資料交易，去中心化，分散式帳本技術}
\clearpage
\setstretch{1.2}

@@

%trustless & automated
%trust: 對系統、對身份、對資料
In data trading platforms, there are three major aspects that need trust: identity, data ownership, and trading. Proving the identity as well as the ownership of data is a challenging issue among various roles in a large scale platform. In current systems, a trusted third-party authority like certificate authority (CA) is widely adopted to certify each member. However, building trust upon CA is dangerous and fragile. The compromise of routers or CA can break the trust of the entire system, and the data portability of using third-party services is still under suspicion. Meanwhile, these concerns are taking into data storage as well, keeping data assets in a centralized data storage or a cloud service meet the constraints of data portability, which may violate the General Data Protection Regulation (GDPR)\cite{GDPR}. Besides CA and storage, the subscription history of data consumers may reveal his/her interests, and the exposure of personal information during the trading process against GDPR as well. The final trust is trading procedures, apart from setting up the agreement between providers and consumers, both of them need to confirm that the agreement will be executed even if one party fails to comply.

@@

Taking all the requirements and the features of streaming data into consideration, the data trading platform for IoT towards a decentralized and trustless design. In this thesis, we investigate the use of a decentralized publish/subscribe (pub/sub) model and DLTs to construct the authority-less and trusted infrastructure. See Fig.~\ref{fig:system_design}. The pub/sub model features the scalability and resource-efficiency, and DLTs resolve the trust of the service, since data and contracts (i.e., smart contracts) written on DLTs are transparent, immutable, and enforced automatically, the digital rights of participants are protected. Lastly, an end-to-end encrypted transmission protocol built on top of DLT is used as data storage, which not only ensures the data integrity but also enables access control and provides a scalable key and data management.

\section{Contributions}
The contributions in the thesis are summarized as follow:
\begin{itemize}
    \item We investigate the usage of DLTs and distributed data storages in order to propose a decentralized architecture for IoT trading and to enable participants to automate the trading procedures and secure digital assets exchange across different organizations.
    \item We apply the subscription-based services economic model to adapt the features of IoT streaming data and clarify the importance of using a decentralized identity system for trading.
    \item We evaluate the performance and concerns of adopting an end-to-end encrypted transmission protocol, and propose an alternative approach for low-level devices to adopt this protocol while ensuring the privacy.
    \item We analyze the cost of the designed smart contract to estimate the minimum data product price for data providers to sustain a product and the minimum cost for data consumers to interact with data products.
\end{itemize}
\clearpage

\section{Thesis Organization}
The rest of this thesis is organized as follows. In Section~\ref{section:relatedWork}, some related work of pub/sub over blockchain, decentralized data trading infrastructures, and distributed data storage are analyzed. In Section~\ref{section:design_thinking}, the components of proposed subscription-based data trading architecture are illustrated. In Section~\ref{section:MAM}, the end-to-end encrypted transmission protocol is introduced along with the protocol delegation solution for low-level devices. In Section~\ref{section:trading_model}, the trading models of proposed architecture are well explained. The analysis results are given in Section~\ref{section:evaluation}. Finally, we conclude the thesis in Section~\ref{section:conclusion} and the future work in Section~\ref{section:future_work}.

@@

\section{The Publish/subscribe Communication Models Over Blockchain}
The pub/sub service model consists of publishers, subscribers, and brokers, which has been proven\cite{pubSubAnalysis, pubSubAnalysis2} to be an efficient and flexible solution for a large number of diverse entities like IoT applications. A lot of work in the pub/sub system built on top of blockchain focused on the reliability, scalability, and the different security issues such as, encrypted data communication, privacy-preserving data subscription, and access control of the digital asset.

@@

In \cite{userCentricData}, the publisher runs a node in blockchain that preserves all the history data of the ledger, therefore, they can publish and manage data without any third-parties. The subscribers request publishers directly and ask them to save a cache space for interesting data. The main contribution of the system is to ensure data owners have full controls of produced data, but the data owners need to have well devices and environments to perform such functionalities and preserve data. Also, the rights for accessing digital assets are more compatible in the IoT scenarios instead of copying raw data. Secure Pub-Sub model\cite{SPS}, a brokerless pub/sub model, is proposed to eliminate the security risk of middleware in the model and to provide a reputation-based fairness payment strategy on blockchain. The privacy and data security are considered thoroughly with the encryption scheme, while the reputation system, the punishment rules against malicious acts of subscribers and publishers, payment, and data sharing are deployed on smart contracts that allow all operations are transparent. Yet, without brokers, providers and subscribers may need to reveal more sensitive information like IP address in order to match both sides. Another broker-less model in \cite{PrivacyPreservPubSub} protects the subscribers' privacy by encrypting users' interests with the light-weight PKEwET\cite{PKEwET}, which allows publishers to match the subscribers' interests in the ciphertext.

@@

\section{Trusted IoT Trading Infrastructure}
Multiple infrastructures for trusted IoT data trading have been proposed. Paolo Missier et. al\cite{MindMyValue} presented an IoT brokered infrastructure based marketplace that enables trading with Ethereum smart contracts. The brokers are only responsible for data transmission in order to adapt flexible agreement between participants. Unlike the standard pub/sub model that matches publishers and subscribers that participants are unaware of each other. However, the data cubes (i.e., a tuple of information, such as provider, subscriber, and time period) are stored in a centralized Cassandra NoSQL database, which is guaranteed to be tamper-proof but the risk of single-point failure still exists.

@@

\section{Distributed Storage System}
\label{section:distributed_storage}
Decentralized storage systems allow users to store files in a distributed network that maintained by individual nodes around the world instead of a central service provider. Nevertheless, DLTs are often used as the backbone of these systems like data storage and also an incentive layer to encourage people to get involved in the network.

@@

\begin{spacing}{2.0}
\label{section:design_thinking}
\section{Data Subscription-based Trading Platform Players}
There are three major roles, data providers, data consumers, and brokers which are similar to the pub/sub messaging model. But unlike the standard pub/sub model where brokers link the publishers and subscribers who are not aware of each other, in our proposed architecture, the brokers are only responsible for message delivery and essential verification processes. As shown in Fig.~\ref{fig:pub_sub_model}.

@@

We adopt the brokered infrastructure for three reasons. Firstly, it inherits the benefits from the standard pub/sub model which is more efficient than the request/response model specifically in a large scale system. Furthermore, if either side is offline, the proceeding tasks have to stop and start over. With brokers, the unfinished work can be cached or accomplished. Second, a fully decentralized architecture has difficulties to brings data providers and consumers together, both of them need to reveal more sensitive information, such as IP address, in order to build the communication tunnel. The existence of brokers resolved the privacy issue, as brokers are the bridges that link data providers and consumers, participants can trade with minimum information like its identifier and public key. Third, a refund process needs a broker to host and supervise the procedures in order to protect the rights of participants, which will be further discussed in Section.~\ref{section:refund}.

\section{Choice of Data Storage}
Data storage is the trust basis of data trading platforms where the data assets are reserved. Streaming data unlike a fixed set of data that can be verified by the hash of the whole pack of data, it consists of continually granular records of each time slot. Therefore, the verification such as, data integrity and source identity is narrow down to a data point as well. In our proposed architecture, we adopt MAM as data storage to resolve the challenges of managing and verifying data streams. MAM is the second layer data communication protocol built on top of IOTA\cite{IOTAwhitepaper} network, the Tangle, a feeless cryptocurrency designed for IoT, which introduces properties like publishing, classifying and tracking authenticated message streams. Carrying these properties, MAM is also appropriate for building a self-sovereign identity system where the identity information such as public key, unique identifiers of services and metadata are stored. One can easily prove himself by sharing the identifier on MAM without any authority.

Currently, considering the efficiency of uploading large files, IPFS performs better than MAM (i.e., writing contents to IOTA network). However, IOTA network scales when more users and transactions join, and the MAM operations can be delegated to powerful proxy servers which will be illustrated in Section.~\ref{section:ta_endpoint}. Furthermore, adopting IPFS in IoT scenarios may meet the challenges of data loss and data retrieving efficiency.

@@

\begin{itemize}
    \item \textbf{Scalability}:
    \begin{itemize}
        \item Benefits from the underlying Tangle network, the system scales when more participants and more transactions join the network.
        \item For both data providers and consumers, MAM keeps the number of managed keys and data entry points as small as possible
    \end{itemize}    
    \item \textbf{Integrity}:
    \begin{itemize}
        \item Messages published to the Tangle are tamper-proof against malicious modifications.
        \item Messages are signed with the keys pre-generated under Merkle signature scheme\cite{MSS} (MSS) that both keys and messages can be verified by participants.
    \end{itemize}
    \item \textbf{Confidentiality}:
    \begin{itemize}
        \item The encrypted data are uploaded that only participants that have keys can decrypt.
        \item The authorized users can retrieve data streams since data is written on the Tangle which can be queried as long as the IOTA network is alive.
        \item MAM provides forward-secrecy. The entry points of future data can be derived, but it's impossible to trace back those in the past. This feature prevents adversaries from retrieving published history even if the key is revealed.
    \end{itemize}
\end{itemize}

@@

\begin{figure}
    \centering
    \includegraphics[width=6.5in]{img/channel_and_key}
    \caption{Within MAM channel, the message publisher has 2 types of key, an encryption key for encrypting contents and a signature key per message for digital signatures. Subscribers can validate the messages with signature keys and decrypt them with the encryption key.}
    \label{fig:channel_and_key}
\end{figure}
\clearpage

\section{Digital Identity}
The digital identity represents entities and holds the digital assets within the digital world, it is important to prove and show the identity to others during interactions. We select the decentralized identity model rather than a centralized one for the concerns in Table.\ref{tab:did}.

@@

\section{Enable Automated Trading Process}
Ethereum is a cryptocurrency building on top of a public blockchain-based distributed ledger. It provides the smart contract, which is a protocol for formulating agreement on a blockchain that running on decentralized virtual machines. A smart contract can interact with other contracts, make decisions, store data, and transfer cryptocurrency. All the participants in Ethereum can verify and execute the contracts, and once the contract is triggered, it is uninterruptible and will be executed automatically without any third-parties.

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=5.5in]{img/smart_contract_mam}
    \caption{The information of identity and data streams are stored on the Tangle with MAM which is all recorded on Product Contracts. Participants can easily retrieve information via the Product Contract and proceed to trade. For signature validation check and further encryption key exchange, the MAM channel ID of participants' DID document are written down, presented in blue color. The orange color stands for the information of data products, which includes the data stream channel/endpoint ID.}
    \label{fig:smart_contract_mam}
\end{figure}
\clearpage

@@

\section{Enable Computation Tasks Delegation to Broker with Privacy}
To manage data products and to benefit from trading, data providers have to interact with MAM and Ethereum smart contract while doing its original tasks. However, the limited resources of low-level devices should be used in their jobs instead of handling all trading processes. Therefore, the operations of MAM and smart contracts are better to be delegated to brokers. The delegation should ensure the privacy of data providers, for instance, brokers are asked to attach messages to MAM and record encryption keys to smart contracts without knowing the contents. The encryption key upload procedure is illustrated in Section.~\ref{section:launch_data_product}.

@@

\section{The Message Streams}
\label{section:mam_streams}
A channel/endpoint is a stream of MAM transaction bundles, which consist of signature and the masked message payload. To publish a MAM message to a channel, MAM deploys MSS to sign the message payload to the channel, where $channel\ ID = root$ i.e., the MSS Merkle root. The Merkle tree is generated with \textbf{seed}, an identifier of its owner in the IOTA protocol, represents the ownership of all things associated with the user in the IOTA ecosystem. Furthermore, the structure of channel/endpoint implements forward linking, each address of a message can be derived from the previous one that other entities can fetch the next payload. This design also brings the advantage of forward secrecy, where no one has access to the data back from his/her entry point. Figure.~\ref{fig:mam_structure} shows the structure of the MAM channel/endpoint.

@@

\section{Enable Access Control and Authentication}
\label{section:mam_functions}
The access control can be enabled via encryption with NTRU\cite{NTRU}, a quantum secure cryptosystem, or Pre-shared key (PSK), to prevent random users retrieving the data from channels. If the message payload is encrypted, subscribers are required for encryption keys to decode messages. The authentication in MAM includes two aspects: source and data. Source authentication ensures the message that originates from the claimed owner, and data authentication ensures the integrity of the data from the sender. These are achieved through the MSS and One-way hash functions by validating the signature added in the signature section of the MAM bundle. However, the size of Merkle Hash Trees, that is, the size of a channel/endpoint should be determined at the start. Thus, data providers need to first decide how to distribute data products into MAM channels/endpoints before uploading data.

\section{The Advantages of Adopting MAM in Subscription-based Data Trading Infrastructure}
\label{section:mam_features}
%scalability
\subsection{A Scalable Keys and Data Entry Points Management}
The importance of scalable key and data entry points management increases over time. In MAM, with an entry point (i.e., the address of transaction) and the encryption key, one can derive the following addresses of the transaction and retrieve data. To manage a data stream, the owner only needs to preserve 1 entry point and 1 encryption key in MAM, but $N$ entry points and 1 encryption key in other distributed storages.
\clearpage

%classify
\subsection{Data Streams Classification and Traceability}
The channel and endpoint structures enable users to be able to easily categorized data streams with respect to different types and usages. For instance, sensor devices like AirBox\cite{LASS}, collect environmental data, can split the statistics like PM 2.5 and humidity by time period into separate channels, which is useful for data providers to organize records and to pack into different data products. As for data traceability, users can easily track the footprints of data change logs as well as checking the validity of modifications with the signature.

\section{Delegate MAM Operations to Tangle-accelerator}
\label{section:ta_endpoint}
MAM builds a secure and authenticated communication protocol on top of multiple cryptosystems, which low-level devices need to spend a lot of resources to apply it, and they may not even support built-in libraries in the regular operating systems. To overcome these concerns, we propose another approach that allows data providers to delegate the MAM operations to Tangle-accelerators, proxy servers with high computation power, which can accelerate the interactions with Tangle while ensuring the privacy of data providers. Fig.~ \ref{fig:ta_struct} shows the structure of Tangle-accelerator, and Fig.~\ref{fig:delegation} shows how data providers can adopt MAM.
\clearpage

@@

\subsection{Communication Protocol}
In the following sections, we refer to the low-level devices as \textbf{endpoint}s. MQTT\cite{MQTT} is chosen as the communication protocol, which requires fewer TCP packets and less traffic. The topic-based pub/sub pattern and lightweight packet that MQTT adopts would undoubtedly play an important role in endpoints with limited bandwidth. The pub/sub model decouples publishers and subscribers in many ways:

@@

\subsection{End-to-End-Encryption}
Introducing a proxy server to process all the cryptographic operations causes the proxy server or the middle man can easily tamper the message. To avoid such malicious operations during transmission, we introduce another lightweight end-to-end-encryption (E2EE) upon MAM protocol. The plaintext will be encrypted with this lightweight end-to-end-encryption. The E2EE process ensures only authorized subscribers can read the messages published on MAM.

%pic
\begin{figure}[h]
    \centering
    \includegraphics[width=6.5in]{img/MAM_E2EE}
    \caption{The process of E2EE.}
    \label{fig:MAM_E2EE}
\end{figure}

In the Fig.~\ref{fig:MAM_E2EE}, we illustrate each step of the presented E2EE process. The details of steps are addressed below:

\begin{enumerate}
    \item Generate symmetric keys with the unique device identifier and Message Authentication Code (MAC) of the previous message. If the message is the first one, then sharing secret initialization information would serve as the MAC of the previous message. Key Derivation Function (KDF) is used to generate the symmetric keys.
    \item Compute the MAC of the current message with the Hash-based Message Authentication Code(HMAC). Both plaintext and the symmetric key would be given as parameters in HMAC.
    \item Apply the generated symmetric key to encrypt the plaintext.
    \item Concatenate the MAC of the current message and the MAC of the previous message, then the result will be signed with a digital signature algorithm.
    \item Send the ciphertext along with the signed MAC.
\end{enumerate}

@@

The E2EE protocol presented in this thesis combines a series of different cryptographic procedures. Each of them can be chosen on the basis of the working hardware and scenario by developers. On certain devices, hardware acceleration would be supported. With hardware-acceleration, the elapsed time could be dropped a step more. For example, applying AES-NI can accelerate AES operations around 40\% on Intel devices.\cite{AES-NI-Acceleration} According to Intel, Table~\ref{tab:AES_NI} shows the performance of Encryption of AES256 with and without hardware acceleration.
